An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-04-25 Article/EconGrowth2.Rnw
CD tri plot now works in the paper. But, graphs are squished horizontally.

# Load historical data
# In Rstudio, this paper is generated from it's directory, which is "Article".
# We need to define paths relative to the location of the paper. 
# Relative path to historical data from Article
baseHistorical <- file.path("..", "data")
historicalData <- Econ2011

@@

\twocolumn{}
<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
  dataCD <- loadAllResampleData(modelType="cd", countryAbbrevsOrder=countryAbbrevs, energyType="none", baseResample=baseResample)
  dataCDQ <- loadAllResampleData(modelType="cde", countryAbbrevsOrder=countryAbbrevs, energyType="Q", baseResample=baseResample)
  data <- rbind.fill(dataCD, dataCDQ)
  standardTriPlot(data=data, facet_formula=countryAbbrev~energy)
@

>>>>

# Load historical data
# In Rstudio, this paper is generated from it's directory, which is "Article".
# We need to define paths relative to the location of the paper. 
# Relative path to historical data from Article
baseHistorical <- file.path("..", "data")
historicalData <- Econ2011 # From the EconData package

@@

\twocolumn{}
<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
  dataCD <- loadAllResampleData(modelType="cd", 
                                countryAbbrevs=countryAbbrevs, 
                                energyType="none", 
                                archive=archive,
                                baseResample=baseResample)
  dataCDQ <- loadAllResampleData(modelType="cde", 
                                 countryAbbrevs=countryAbbrevs, 
                                 energyType="iQ", 
                                 archive=archive,
                                 baseResample=baseResample)
  data <- rbind.fill(dataCD, dataCDQ)
  standardTriPlot(data=data, facet_formula=countryAbbrev~energyType)
@
